Active Learning for SAT Solver Benchmarking

### 2022-10-10 paper/paper.tex
section3.2

We transform the runtimes into discrete runtime classes which are determined on a per instance basis.
For each instance $e \in \mathcal{I}$, we use a single-link hierarchial clustering algorithm to assign the runtimes in $\{ r(a, e) \mid a \in A \}$ to one of the $k$ clusters $C_1, \dots, C_k$.
Without loss of generality, the fastest runtimes for instance $e$ are in cluster $C_1$ and the slowest are in cluster $C_k$.
For instances with many timeouts, we have to manually fix the clustering results such that all timeouts $\tau$ are in cluster $C_k$.
The runtime transformation function $\gamma_k : {\mathcal{A} \times \mathcal{I}} \rightarrow \left\lbrace 1, \dots, k \right\rbrace$ is then specified as follows.
$$\gamma_k(a, e) = j ~\Leftrightarrow~ r(a, e) \in C_j$$

@@

To determine solver ranks, we define the adapted scoring function $s_k : A \rightarrow [1, 2 \cdot k]$ as follows.
\begin{align*}
  s_k(a) := \frac{1}{|\mathcal{I}|} \sum_{e \in \mathcal{I}} \gamma'_k(a, e)
  &&
  \gamma'_k(a, e) := \begin{cases}
  	2 \cdot \gamma_k(a, e) 	& \text{if } \gamma_k(a, e) = k\\
	\gamma_k(a, e)	& \text{otherwise}
  \end{cases}
  \label{eq:rankingeq}
\end{align*}

@@

\subsection{Instance Sampling}
\label{sec:main-sampling}
Our instance-sampling strategies (also refer to Algorithm~\ref{algALBenchmark}; line 4) can be divided into two categories.
First, we present possible baseline approaches including existing work on instance-based selection strategies~\cite{Bossek021a,GentHJKMNN14,MatriconAFSH21}.
Second, we show promising machine-learning-based sampling strategies that make use of the model's label-prediction function $f$ and are inspired by existing work within the realms of active learning~\cite{settles2009active}.

>>>>

We transform the runtimes into discrete runtime classes which are determined on a per instance basis.
For each instance $e \in \mathcal{I}$, we use a single-link hierarchial clustering algorithm to assign the runtimes in $\bigl\{ r(a, e) \mid a \in A \bigr\}$ to one of the $k$ clusters $C_1, \dots, C_k$ such that the fastest runtimes for instance $e$ are in cluster $C_1$ and the slowest are in cluster $C_k$.
For instances with many timeouts, we have to manually fix the clustering results such that all timeouts $\tau$ are in cluster $C_k$.
The runtime transformation function $\gamma_k : {\mathcal{A} \times \mathcal{I}} \rightarrow \left\lbrace 1, \dots, k \right\rbrace$ is then specified as follows.
$$\gamma_k(a, e) = j ~\Leftrightarrow~ r(a, e) \in C_j$$

@@

To determine solver ranks, we use the transformed runtimes $\gamma_k(a, e)$ in the adapted scoring function $s_k : A \rightarrow [1, 2 \cdot k]$ as follows.
\begin{align*}
  s_k(a) := \frac{1}{|\mathcal{I}|} \sum_{e \in \mathcal{I}} \gamma'_k(a, e)
  &&
  \gamma'_k(a, e) := \begin{cases}
  	2 \cdot \gamma_k(a, e) 	& \text{if } \gamma_k(a, e) = k\\
	\gamma_k(a, e)	& \text{otherwise}
  \end{cases}
  \label{eq:rankingeq}
\end{align*}

@@

\subsection{Instance Sampling}
\label{sec:main-sampling}

Our instance-sampling strategies (also refer to Algorithm~\ref{algALBenchmark}; line 4) can be divided into two categories.
First, we present possible baseline approaches including existing work on instance-based selection strategies~\cite{Bossek021a,GentHJKMNN14,MatriconAFSH21}.
Second, we show promising machine-learning-based sampling strategies that make use of the model's label-prediction function $f$ and are inspired by existing work within the realms of active learning~\cite{settles2009active}.
